Static contract checking for Haskell

### 2011-10-27 paper.tex
Wibble.

  Here's a flawed contradiction ``proof'': consider
  \[
  e = e ::: CF \&\& \neg CF.
  \]
  Now, $T$ will contain $CF(ep) \land \neg CF(ep)$, and were hosed.
  This is flawed because there is no $\neg$ in the annotated
  contracts.

@@

\begin{itemize}
\item $(\Phi_1)$ For each $K_i$ of arity $a_i$ we introduce selectors
  $sel_{k,K_i}$, which are the projection of $K_i(x_1,\dots,x_{a_i})$
  on its $k$-th component, $k = 1\text{ to }a_i$.
\item $(\Phi_2)$ For each pair of constructors $K_i,K_j$, $i \not = j$, we state that they can
  never map to the same value.
\item $(\Phi_3)$ Then, we have to give crash-freeness conditions for each $K_i$:
  Notice that we have a equivalence.
  \begin{itemize}
  \item $\leftarrow$: if we pack crash-free values in a data
    constructor, the resulting value is crash-free.
  \item $\rightarrow$: a value $t$ of type $T$\note[nc]{
    ``type'' is used loosely here: it means the constructor head is of type $T$.
    } is crash-free implies
    that every value packed in it is crash-free. Recall that one can
    define projection on any argument of a value of type $t$. So if
    the $k$-th argument of $t$ is not crash-free, then the $k$-th
    projection is a crash-free context that throws an expression that
    is not crash-free.

>>>>

  Here's a flawed contradiction ``proof'': consider
  \[
  e = e ::: CF \&\& \lnot CF.
  \]
  Now, $T$ will contain $CF(ep) \land \lnot CF(ep)$, and were hosed.
  This is flawed because there is no $\lnot$ in the annotated
  contracts.

@@

\begin{itemize}
\item $(\Phi_1)$ For each $K_i$ of arity $a_i$ we introduce selectors
  $sel_{k,K_i}$, which are the projection of $K_i(x_1,\dots,x_{a_i})$
  on its $k$-th component, $k = 1\text{ to }a_i$.
\item $(\Phi_2)$ For each pair of constructors $K_i,K_j$, $i \not = j$, we state that they can
  never map to the same value.
\item $(\Phi_3)$ Then, we have to give crash-freeness conditions for each $K_i$:
  Notice that we have a equivalence.
  \begin{itemize}
  \item $\gets$: if we pack crash-free values in a data
    constructor, the resulting value is crash-free.
  \item $\to$: a value $t$ of type $T$\note[nc]{
    ``type'' is used loosely here: it means the constructor head is of type $T$.
    } is crash-free implies
    that every value packed in it is crash-free. Recall that one can
    define projection on any argument of a value of type $t$. So if
    the $k$-th argument of $t$ is not crash-free, then the $k$-th
    projection is a crash-free context that throws an expression that
    is not crash-free.
